Adolescent well-being in the digital age

### 2022-01-10 index.qmd
Split into sections

---
title: "Adolescent well-being in the digital age"
author: "Matti Vuorre"
date: "`r Sys.time()`"
execute:
  eval: true
  error: true
  cache: true
  warning: false
  message: false
format: 
  html:
    monofont: Fira Code
    font-size: 1.0em
    linestretch: 1.4
    code-fold: true
    code-summary: "Show code"
    code-tools: true
    code-link: true
toc: true
toc-depth: 4
toc-title: Contents
number-sections: false
crossref:
  fig-prefix: Figure
  tbl-prefix: Table
---

```{r document-options, include = FALSE, cache = FALSE}
# knitr options
knitr::opts_chunk$set(
  fig.align = "center",
  cache.lazy = FALSE # Fix large knitr cache
)
```

## Preface

Welcome! This document is the online analysis supplement to *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, [Preprint]() in preparation). It contains all the analyses reported in the manuscript along with supplemental analyses. The source code and the underlying data are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), with an archived permanent copy on [OSF](https://osf.io/ys7m9/).

::: {.callout-note collapse="true"}
### Reproducibility

@@

1.  Clone the github repo

-   Terminal: `git clone https://github.com/digital-wellbeing/global-wbmh.git`
-   RStudio: File -> New Project -> Version Control -> Git -> use the URL from above

2.  Prepare the R environment

-   Terminal: `Rscript -e "renv::restore()`
-   RStudio: Click renv -> Restore Library in the Packages panel

3.  Render `index.qmd` to `index.html`

-   Install [Quarto](https://quarto.org/docs/getting-started/installation.html) if you don't already have it
-   Terminal: `quarto render index.qmd`
-   RStudio: Open `index.qmd` and click Render

The models take several hours each to run---depending on your local computing resources---and therefore the rendering process can take several days.

If something doesn't work please open an issue at <https://github.com/digital-wellbeing/global-wbmh/issues>.
:::

## Data preparation

Our analyses draw on three sources of data. The Gallup World Poll is a proprietary dataset and includes people's responses to well-being questions across \~160 countries from 2015 to 2021. The Global Burden of Disease dataset consists of mental health indicators across \~200 countries from 2000 to 2019. And finally the International Telecommunications Union dataset has internet adoption metrics across \~200 countries from 2000 to 2020.

In this first section, we load the raw data sets and prepare them for analyses. We first set up the R environment with these packages and settings:

```{r setup, cache = FALSE}

# Packages
library(readxl)
library(knitr)
library(ragg)
library(imputeTS)
library(naniar)
library(scales)
library(janitor)
library(haven)
library(labelled)
library(countrycode)
library(ggtext)
library(dtplyr)
library(lubridate)
library(kableExtra)
library(gtsummary)
library(ggstance)
library(mgcv)
library(brms)
library(cmdstanr)
library(ellipse)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(posterior)
library(parameters)
library(emmeans)
library(broom)
library(kableExtra)
library(tidyverse)

# MCMC settings (ensure at most 12 cores)
ncores <- min(parallel::detectCores(logical = FALSE), 12)
nchains <- 4
options(brms.backend = "cmdstanr")
hmc <- list(
  chains = nchains,
  cores = nchains,
  threads = ncores %/% nchains,
  iter = 2500,
  warmup = 1000,
  refresh = 50,
  adapt_delta = .90,
  max_treedepth = 10
)

# Plotting theme & use this font if available
Font <- "Titillium Web"
theme_set(
  theme_linedraw(
    base_size = 12,
    base_family = Font
  ) +
    theme(
      panel.grid = element_blank(),
      strip.text = element_text(margin = margin(4, 4, 4, 4, "pt"))
    )
)

# Format tables
kable_custom <- function(x) {
  kable_classic(
    kable_input = x,
    html_font = Font,
    font_size = 13,
    lightable_options = "striped",
    position = "center",
    full_width = FALSE
  )
}

# Create directory for intermediate files
dir.create("models", FALSE)
```

### Gallup World Poll

We first prepare the Gallup data. Note that this data set is not publicly available, and therefore not included in our repository. We provide a synthetic mock dataset---loaded below---for users who do not have access to the GWP dataset.

```{r gallup-codebook}
#| echo: false
#| eval: false
# Understand variables & values
# Codes NOTE 1: yes 2: no!
read_spss(
  "data-raw/Gallup/The_Gallup_101521.sav",
  n_max = 1,
  col_select = c(
    WPID, WP1219,
    WP16,
    WP60, WP61, WP63, WP65, WP67,
    WP68, WP69, WP70, WP71, WP74
  )
) %>%
  generate_dictionary()
```

Here we import the relevant variables from Gallup's SPSS files and then

-   Clean the variable names
-   Set appropriate missing values (`NaN`, not e.g. `-99`)
-   Use appropriate coding schemes (e.g. 0: no; 1: yes)
-   Calculate scale scores (means over items)
-   Rescale outcomes to proportions (0 - 1)
-   Subset the data to 15 to 24 year olds
-   Create age-categories in line with GBD data
-   Drop one 13 year old as this data should only have people 15 and older

```{r gallup-clean}
# First liberate the data from the slow SPSS file and save to disk
gwp_path <- "data-raw/Gallup/gwp-processed.rds"
if (!file.exists(gwp_path)) {
  gwp <- read_spss(
    "data-raw/Gallup/The_Gallup_101521.sav",
    col_select = c(
      YEAR_CALENDAR,
      COUNTRYNEW,
      WPID, WP1220, WP1219,
      WP16,
      WP60, WP61, WP63, WP65, WP67,
      WP68, WP69, WP70, WP71, WP74
    )
  )

  # Get rid of SPSS attributes
  gwp <- gwp %>%
    zap_labels() %>%
    zap_label() %>%
    zap_widths() %>%
    zap_formats()

  # Save into a good format
  write_rds(gwp, gwp_path)
} else {
  gwp <- read_rds(gwp_path)
}

gwp <- gwp %>%
  clean_names() %>%
  transmute(
    country = countrynew,
    year = year_calendar,
    id = wpid,
    sex = factor(wp1219, levels = c(2, 1), labels = c("Female", "Male")),
    age = wp1220,
    # Don't know, refused, and missing values
    Life_satisfaction = if_else(between(wp16, 0, 10), wp16, NaN),
    across(wp60:wp74, ~ if_else(between(., 1, 2), ., NaN)),
    # Also reverse the weird 1: yes 2: no coding here
    across(wp60:wp74, ~ 3 - .)
  )

# Scale scores note rescaling
gwp <- gwp %>%
  mutate(
    Life_satisfaction = Life_satisfaction / 10,
    Negative_experiences =
      rowMeans(select(., wp68:wp74), na.rm = TRUE) - 1,
    Positive_experiences =
      rowMeans(select(., wp60:wp67), na.rm = TRUE) - 1
  ) %>%
  select(-c(wp60:wp74))

# Categorize ages
gwp <- gwp %>%
  mutate(
    age = cut(
      age,
      breaks = seq(15, 105, by = 5),
      include.lowest = TRUE,
      right = FALSE,
      labels = paste(seq(15, 100, by = 5), "to", seq(19, 104, by = 5))
    ) %>% as.character()
  )

# There is one 13 year old which resulted in a NA and we drop it
gwp <- drop_na(gwp, age)

# Focus on young people
gwp <- gwp %>%
  filter(age %in% c("15 to 19", "20 to 24"))
```

Instead of working with the person-level scale scores, we aggregate the data to means and standard errors for each cell as defined by the predictors (country, year, age, sex). Because we treat outcomes as normal this greatly simplifies and speeds up the computations without affecting the results, and also makes the data format concordant with the GBD data.

```{r gallup-summarise}
gwp <- gwp %>%
  pivot_longer(
    c(
      Life_satisfaction,
      Negative_experiences,
      Positive_experiences
    ),
    names_to = "outcome", values_to = "val"
  ) %>%
  group_by(country, year, sex, age, outcome) %>%
  summarise(
    se = sd(val, na.rm = TRUE) / sqrt(n()),
    val = mean(val, na.rm = TRUE)
  ) %>%
  ungroup()
```

We have three data sets with information on countries. Unfortunately, they can all use idiosyncratic naming conventions for the countries, and we therefore harmonise the names in each dataset to the same standard values. We use the short English names from the UNICODE CLDR project as provided by `countrycode::countryname()`. We do that here for the GWP data, and check that all countries receive a unique name.

```{r gwp-harmonise-countries}
#| results: hold
#| label: tbl-gwp-countries
#| tbl-cap: "Countries whose original GWP name is different to the harmonised one, or whose harmonised name is missing"
#| layout-ncol: 1

# Check what names were changed and if any don't have harmonised counterpart
gwp %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl(caption = "GWP harmonised country names") %>%
  kable_custom()

# We can see that this would result in North Cyprus being lumped with Cyprus so we need to replace the name before harmonising

# Harmonise old names and replace only if harmonised name found
gwp <- gwp %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  # Prevent north cyprus from becoming cyprus
  mutate(
    country_harmonised = ifelse(
      country == "Northern Cyprus",
      "Northern Cyprus",
      country_harmonised
    )
  ) %>%
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)
```

### Global Burden of Disease

We downloaded the Global Burden of Disease data from <http://ghdx.healthdata.org/gbd-results-tool> on 2021-11-02 to `data-raw/GBD/`. We include those files in our repository as [permitted by the license](http://ghdx.healthdata.org/): We load all the GBD tables to R. They are inside downloaded `.zip` files, of which there may be more than one.

```{r gbd-data-load}
# Load data files and merge to one table
gbd <- list.files(
  "data-raw/GBD/",
  pattern = ".zip", full.names = TRUE, recursive = TRUE
) %>%
  read_csv()
```

We then clean the GBD data and

-   Clean the variable names
-   Remove the metric and measure variables; we focus on prevalence rate
    -   prevalence: Total number of cases
    -   rate: Total cases per 100,000 population
-   Convert outcome rates to proportions (0 - 1)
-   Clean cause names and rename to outcome to harmonise with GWP
-   Convert GBD estimated rate CI limits to an approximate standard error
-   Subset data to young people (10 - 24)

```{r gbd-data-clean}
# First step is to clean names
gbd <- clean_names(gbd)

# Confirm that correct measures were downloaded:
# distinct(gbd, measure, metric)
gbd <- select(gbd, -metric, -measure)
gbd <- gbd %>%
  mutate(across(c(val, upper, lower), ~ .x / 100000))

# Clean cause names
# distinct(gbd, cause)
gbd <- gbd %>%
  mutate(
    cause = case_when(
      cause == "Anxiety disorders" ~ "Anxiety",
      cause == "Depressive disorders" ~ "Depression",
      cause == "Self-harm" ~ "Selfharm"
    )
  )

# Harmonise variable names with other datasets
gbd <- gbd %>%
  rename(country = location, outcome = cause)

# The outcomes values are model predictions and come with lower and upper CI limits (2.5 and 97.5 %iles of their posterior distributions). We convert those to normal approximate standard errors.
gbd <- gbd %>%
  mutate(se = (upper - lower) / (1.96 * 2)) %>%
  select(-c(upper, lower))

# Focus on young people
gbd <- gbd %>%
  filter(age %in% c("10 to 14", "15 to 19", "20 to 24"))
```

Then we need to harmonise to country names (always somewhat idiosyncratic) to a common metric. There is a harmonised name for each GBD country, and 27 country names are harmonised.

```{r gbd-harmonise-countries}
#| results: hold
#| label: tbl-gbd-countries
#| tbl-cap: "Countries whose original GBD name is different to the harmonised one, or whose harmonised name is missing"
#| layout-ncol: 1

# Check what names were changed and if any don't have harmonised counterpart
gbd %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl(caption = "GBD harmonised country names") %>%
  kable_custom()
# Harmonise old names and replace only if harmonised name found
gbd <- gbd %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)
```

### International Telecommunication Union

After processing the outcome tables above, we move on to the internet adoption metrics from the ITU. We downloaded these data files from the ITU website. New versions may be posted subsequent to this, in which case the URLs could be changed here to update the analyses with latest data.

After downloading, we cleaned the ITU data to a shape concordant with the outcome data, and converted the values to proportions (0 - 1). Then we harmonised the country names as above, and dropped countries that don't exist in outcomes.

```{r itu-process}
#| results: hold
#| label: tbl-itu-0
#| tbl-cap: "ITU countries"
#| layout-ncol: 1

# Download data sets from the ITU website if not yet downloaded
if (!file.exists("data-raw/ITU/PercentIndividualsUsingInternet.xlsx")) {
  dir.create("data-raw/ITU")
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/PercentIndividualsUsingInternet_Nov2021.xlsx",
    "data-raw/ITU/PercentIndividualsUsingInternet.xlsx"
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/FixedBroadbandSubscriptions_2000-2020.xlsx",
    "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx"
  )
  download.file(
    "https://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2021/July/MobileBroadbandSubscriptions_2007-2020.xlsx",
    "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx"
  )
}

# Read and reshape fixed broadband data
itu_fixed <- read_xlsx(
  "data-raw/ITU/FixedBroadbandSubscriptions_2000-2020.xlsx",
  sheet = 2,
  col_types = "text"
) %>%
  pivot_longer(-c(Indicator, Country)) %>%
  separate(name, into = c("year", "variable")) %>%
  pivot_wider(names_from = variable) %>%
  mutate(fixed = as.numeric(value)) %>%
  select(country = Country, year, fixed)

# Read and reshape mobile broadband data
itu_mobile <- read_xlsx(
  "data-raw/ITU/MobileBroadbandSubscriptions_2007-2020.xlsx",
  sheet = 2,
  col_types = "text"
) %>%
  pivot_longer(-c(Indicator, Country)) %>%
  separate(name, into = c("year", "variable")) %>%
  pivot_wider(names_from = variable) %>%
  mutate(mobile = as.numeric(value)) %>%
  select(country = Country, year, mobile)

# Percent using internet
itu_percent <- read_xlsx(
  "data-raw/ITU/PercentIndividualsUsingInternet.xlsx",
  col_types = "text"
) %>%
  pivot_longer(-c(Indicator, Country)) %>%
  separate(name, into = c("year", "variable")) %>%
  pivot_wider(names_from = variable) %>%
  mutate(internet = as.numeric(value)) %>%
  select(country = Country, year, internet)

# Merge to one table in wide format (oldest on left to include all years)
itu <- reduce(list(itu_percent, itu_fixed, itu_mobile), left_join)

# values (1-100) to proportions (0-1) and years to numbers
itu <- itu %>%
  mutate(across(c(internet, fixed, mobile), function(x) x / 100)) %>%
  mutate(year = as.numeric(year))

# Drop tables
rm(itu_fixed, itu_mobile, itu_percent)

# Harmonise countries
# Check what names were changed and if any don't have harmonised counterpart
itu %>%
  distinct(country) %>%
  arrange(country) %>%
  mutate(
    country_harmonised = countryname(country, destination = "cldr.short.en")
  ) %>%
  filter(country != country_harmonised | is.na(country_harmonised)) %>%
  kbl(caption = "ITU harmonised country names") %>%
  kable_custom()

# Harmonise old names and replace only if harmonised name found
itu <- itu %>%
  mutate(
    country_harmonised = countryname(
      country,
      destination = "cldr.short.en"
    )
  ) %>%
  # This picks the harmonised name if exists, otherwise original name
  mutate(country = coalesce(country_harmonised, country)) %>%
  select(-country_harmonised)

# Drop countries that don't exist in outcomes
itu <- itu %>%
  filter(
    country %in% unique(gbd$country) | country %in% unique(gwp$country)
  )

# Drop countries that don't have any actual internet data
itu_zeros <- itu %>%
  group_by(country) %>%
  summarise(s = sum(internet, na.rm = TRUE)) %>%
  filter(s == 0)

itu <- itu %>%
  filter(!(country %in% itu_zeros$country))
rm(itu_zeros)
```

#### Missingness

We then impute missing intermediate values to the internet adoption timeseries. We use linear interpolation to fill missing intermediate values, but do not extrapolate before or after the first and last values of each country.

```{r itu-impute}
#| results: hold
#| label: tbl-itu-impute
#| tbl-cap: "Summary of ITU data imputation"

# Reshape to easily impute all variables
itu_long <- itu %>%
  pivot_longer(c(internet, fixed, mobile))

# Impute by country and variable
itu_long <- itu_long %>%
  group_by(country, name) %>%
  # Find first and last year with this variable in each country
  # so as to prevent extrapolation
  mutate(
    min_year = year[min(which(!is.na(value)))],
    max_year = year[max(which(!is.na(value)))]
  ) %>%
  # Interpolate values linearly
  # use possibly() to avoid errors for countries with no data
  mutate(
    across(
      value,
      .fns = list(
        i = possibly(
          function(x) na_interpolation(x, maxgap = Inf),
          otherwise = NaN
        )
      )
    )
  ) %>%
  # Take out projected (non-intermediate) imputed values
  mutate(
    value_i = if_else(
      between(year, unique(min_year), unique(max_year)),
      value_i,
      NaN
    )
  ) %>%
  ungroup() %>%
  select(-min_year, -max_year)

# Summary
itu_long %>%
  group_by(name) %>%
  mutate(min_year = if_else(name == "mobile", 2007, 2000)) %>%
  summarise(
    n_miss_orig = sum(is.na(value) & year >= min_year),
    p_miss_orig = percent(n_miss_orig / sum(year >= min_year), .1),
    n_miss_imp = sum(is.na(value_i) & year >= min_year),
    p_miss_imp = percent(n_miss_imp / sum(year >= min_year), .1),
    imputed = n_miss_orig - n_miss_imp
  ) %>%
  kbl(caption = "ITU data imputation summary") %>%
  kable_custom()

# We then replace the original values with the imputed ones
itu <- itu_long %>%
  # Pick non-missing value, from original and imputed
  mutate(value = coalesce(value, value_i)) %>%
  select(-value_i) %>%
  pivot_wider()
rm(itu_long)
```

### GLOBE regions

We group the countries into GLOBE regions in order to have a higher level of grouping at which the analyses can be summarised. This allows us to eg. present figures and tables per region, instead of overwhelmingly by country, and also provides an upper level for the multilevel models. We use the extended GLOBE regions following Jebb et al. (2020), and had to manually add labels to some countries that were not grouped in those studies.

```{r globe-regions}
#| results: hold
#| label: tbl-globe
#| tbl-cap: "Countries with manually filled region"

regions <- read_csv(
  "data-raw/Regions/GLOBE-regions-from-Jebb-et-al-2020.csv"
) %>%
  # Jebb et al used * to indicate deviance from GLOBE, remove
  mutate(country = str_remove_all(country, "\\*")) %>%
  # Standardize country names
  # This drops Nagorno-Karabakh Republic
  mutate(country = countryname(country)) %>%
  drop_na(country)

# This also combined Swaziland and (Eswatini) to Eswatini, and Northern- and Cyprus. Therefore we just take the distinct country & region.
regions <- distinct(regions, region, country)

# Countries in GBD not present in region data
no_region_gbd <- filter(
  distinct(gbd, country),
  !(country %in% unique(regions$country))
) %>%
  arrange(country)

# Then see what countries in GWP are without region
no_region_gwp <- filter(
  distinct(gwp, country),
  !(country %in% unique(regions$country))
) %>%
  arrange(country)

bind_rows(no_region_gbd, no_region_gwp) %>%
  arrange(country) %>%
  distinct() %>%
  write_csv("data-raw/Regions/countries-without-region.csv")

# I then filled missing regions in Jebb et al and extended GLOBE referenced therein

# Load our manually filled region data
regions_filled <- read_csv(
  "data-raw/Regions/countries-without-region-filled.csv"
)

# Combine Jebb et al GLOBE regions and our manually added ones
regions <- regions %>%
  bind_rows(
    regions_filled %>%
      mutate(Note = "Filled")
  ) %>%
  arrange(region, country)

# Shorter name for plots
regions <- regions %>%
  mutate(region = if_else(region == "Sub-Sahara Africa", "Africa", region))

# Display table of regions and countries
regions %>%
  drop_na(Note) %>%
  select(-Note) %>%
  arrange(region, country) %>%
  kbl(caption = "Countries with a manually filled region") %>%
  kable_custom()

# Clean region labels
regions$region <- str_replace_all(regions$region, " ", "_")
regions$region <- factor(regions$region)

# Remove unnecessary items
regions <- select(regions, -Note)

# Add regions to data tables
itu <- left_join(itu, regions)
gbd <- left_join(gbd, regions)
gwp <- left_join(gwp, regions)
# Remove now unnecessary variables
rm(no_region_gbd, no_region_gwp, regions_filled, regions)
```

### ITU summary table

```{r itu-summary-table}
#| column: page
#| tbl-cap: "Mean internet user percentages across regions and time."
#| label: tbl-itusummary

itu %>%
  select(region, country, year, internet) %>%
  mutate(internet = internet * 100) %>%
  mutate(region = str_replace(region, "_", " ")) %>%
  pivot_wider(names_from = year, values_from = internet) %>%
  select(-country) %>%
  tbl_summary(
    by = region,
    missing = "no",
    statistic = list(all_continuous() ~ "{mean}% ({N_nonmiss})")
  ) %>%
  add_overall(col_label = "Total") %>%
  as_kable_extra(caption = "ITU summary") %>%
  row_spec(0, bold = TRUE) %>%
  kable_custom()
```

## RQ1: Time courses

Our first research question concerns changes in mental health and well-being over time: To what extent has adolescent mental health changed over time (RQ1a)? And, do changes in well-being correlate with changes in internet adoption (RQ1b)? To answer, we estimate a multilevel multivariate model of the outcomes and internet adoption.

### Modelling

We first prepare the variables for modelling:

-   Transform edge values of internet variable to fit beta
    -   2 values were changed (0 in Timor-Leste in 2002, and 1 in UAE 2020)
-   Join outcome and predictor tables
-   Center year on 2010 (roughly in the middle)
-   Ensure that age and sex are treated with contrast codes

```{r model1-prepare-data}
# Transform internet edge cases
itu <- itu %>%
  mutate(internet = if_else(internet == 0, .0000001, internet)) %>%
  mutate(internet = if_else(internet == 1, .9999999, internet))

# Stack outcome data
dat <- bind_rows(gwp, gbd)

# Merge predictors to outcomes
dat <- left_join(dat, itu)

# Center and scale year
dat <- dat %>%
  mutate(year = (year - 2010) / 10)

# Identify values to use in mv models
# Indicate unique ITU values for MV model
dat <- dat %>%
  # Unique values exist for each country-year, but must be given for each
  # outcome
  group_by(region, country, year, outcome) %>%
  mutate(itu = 1:n() == 1) %>%
  ungroup()

# Ensure that factors are contrast coded
dat <- dat %>%
  mutate(across(c(sex, age), factor))
options(contrasts = c(unordered = "contr.sum", ordered = "contr.poly"))

# Model outcomes on the percentage (0-100) scale. Note internet is still 0-1
dat <- dat %>%
  mutate(across(c(val, se), ~ . * 100))

# Arrange on outcome
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
dat <- dat %>%
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  arrange(dat, outcome, region, country, year)

dat %>%
  group_by(outcome) %>%
  summarise(
    min = min(val, na.rm = TRUE),
    max = max(val, na.rm = TRUE),
    internet_min = min(internet, na.rm = TRUE),
    internet_max = max(internet, na.rm = TRUE)
  ) %>%
  kable(digits = 7) %>% 
  kable_custom()
```

#### Specification

We first tackle RQ1: To what extent did the outcomes change over time (1a), and were changes in outcomes correlated with changes in internet adoption between countries (1b). Model 1, a three-level bayesian meta-regression model, will provide answers, by simultaneously estimating trends over time for the outcome (e.g. Life satisfaction) and internet adoption, with shared covariance matrices over the two outcomes across regions and countries. We also include contrast-coded demographic factors as main effects and moderators, and can therefore examine whether the trends differ between demographic groups (RQ3)

We fit the model separately for each outcome. Although a full multivariate would additionally allow examining correlations in time trends of the outcomes, it is not plausible with the differential groups in the data sets (contrast coded demographic groups would be harder to interpret). We therefore estimate six separate bivariate models

In this model, internet adoption is treated as Beta-distributed and the outcomes are treated as gaussian. All the regression coefficients are allowed to vary randomly across regions and countries, with a shared correlation matrix of the random effects across the two model outcomes. This latter specification is important to allow answering RQ1b.

The GBD data are estimates with standard errors, and thus suggest that a model that incorporates the SEs would be appropriate. For this reason, and for reducing computational complexity, we have reshaped the GWP data similarly to aggregates per cell (mean and SE for each country \* year \* sex \* age). The one downside of this modelling strategy is that it does not converge for self-harm, probably because the means and SEs are highly correlated in those data. Therefore we estimate the model with SEs for all outcomes except self-harm, where we set the SEs to zero, leading to a regular (three-level) regression model.

We write the model as

$$
\begin{align*}
y_i &\sim \text{Normal}(\mu^y_i, \sigma^{2y}v_i) \\
\mu^y_i &= \beta^{y}_{0} + \delta^{y}_{0\text{region}[i]} + 
\gamma^{y}_{0\text{country}[i]} + \\ &(\beta^y_{1} + \delta^{y}_{1\text{region}[i]} + \gamma^{y}_{1\text{country}[i]})\text{Time}_i + 
\\ &(\beta^y_{2} + \delta^{y}_{2\text{region}[i]} + \gamma^{y}_{2\text{country}[i]})\text{Sex}_i + 
\\ &(\beta^y_{3} + \delta^{y}_{3\text{region}[i]} + \gamma^{y}_{3\text{country}[i]})\text{Age}_i + 
\\ &(\beta^y_{4} + \delta^{y}_{4\text{region}[i]} + \gamma^{y}_{4\text{country}[i]})\text{Sex}_i \times \text{Time}_i + 
\\ &(\beta^y_{5} + \delta^{y}_{5\text{region}[i]} + \gamma^{y}_{5\text{country}[i]})\text{Age}_i \times \text{Time}_i \\ \\
x_i &\sim \text{Beta}(\mu^x_i, \phi^x) \\ 
\text{logit}(\mu^x_i) &= \beta^{y}_{0} + \delta^{x}_{0\text{region}[i]} + \gamma^{x}_{0\text{country}[i]} + \\ &(\beta^x_{1} + \delta^{x}_{1\text{region}[i]} + \gamma^{x}_{1\text{country}[i]})\text{Time}_i  \\ \\
\left[\begin{array}{c}
\delta^y_{0\text{region}} \\ \delta^y_{1\text{region}} \\ 
\delta^y_{2\text{region}} \\ \delta^y_{3\text{region}} \\ 
\delta^y_{4\text{region}} \\ \delta^y_{5\text{region}} \\ 
\delta^x_{0\text{region}} \\ \delta^x_{1\text{region}}
\end{array}\right] 
&\sim MVN(
\mathbf{0},
\Sigma^\text{r}
),
\left[\begin{array}{c}
\gamma^y_{0\text{country}} \\ \gamma^y_{1\text{country}} \\ 
\gamma^y_{2\text{country}} \\ \gamma^y_{3\text{country}} \\ 
\gamma^y_{4\text{country}} \\ \gamma^y_{5\text{country}} \\ 
\gamma^x_{0\text{country}} \\ \gamma^x_{1\text{country}}
\end{array}\right] 
\sim MVN(
\mathbf{0},
\Sigma^\text{c}
)
\end{align*}
$$

Where $y_i$ are the outcomes, $x_i$ the internet adoption values, and $v_i$ indicate the known sampling variances.

We then define the model formulas in brms' formula syntax. First, for internet adoption, we take care to indicate that each internet adoption datum should be modelled only once, because the values are repeated in the outcome data table. To do this we use `resp_subset(itu)`, where `itu` indicates first unique rows of ITU data in the model. The `|c|` and `|r|` separating the random effects from their grouping factors indicate shared correlation matrices with other modelled parameters in the model (see the next model formula below).

```{r model1-itu-bf}
# Define a model of internet proportion over year
bf_itu <- bf(
  internet | resp_subset(itu) ~
  year +
    (year |c| country) +
    (year |r| region),
  family = Beta()
)
```

Here, we specify the outcome model. Note the `|c|` and `|r|` that link the countries' and regions', respectively, random effects of this model with the previous' model. Then, we specify `resp_se(se, sigma = TRUE)` to enable "meta-regression" with known standard errors. In addition, it leads to the residual variance to be estimated.

```{r model1-val-bf}
# Meta-regression model of outcomes
bf_1 <- bf(
  val | resp_se(se, sigma = TRUE) ~
  year * sex + year * age +
    (year * sex + year * age | c | country) +
    (year * sex + year * age | r | region),
  family = gaussian()
)
```

Finally, after numerous attempts we were unable to fit a model with meta-analytic standard errors with self-harm as the outcome in a way that would have converged. We therefore effectively removed the SEs from self-harm by setting them to zero

```{r model1-selfharm-se}
dat <- dat %>% 
  mutate(se = if_else(outcome == "Selfharm", 0, se))
```

#### Fitting

We then create a table where each row is a dataset and a model to be fitted, and then fit the models row-by-row. This takes about a day for the six outcomes.

```{r fit-model-1}

fits <- dat %>%
  # Could nest but need this to include group key in nested tibble
  group_by(outcome) %>%
  summarise(data = list(cur_data_all()))

fits <- fits %>%
  mutate(
    fit1 = map2(
      data, outcome,
      ~brm(
        formula = bf_itu + bf_1 + set_rescor(FALSE),
        data = .x,
        chains = hmc$chains,
        cores = hmc$cores,
        threads = hmc$threads,
        iter = hmc$iter,
        warmup = hmc$warmup,
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta,
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("models/brm-{.y}-1-internet")
      )
    )
  )
```

#### Summary

Here is a summary of the data modelled for each outcome

```{r model-1-data-summary}
#| column: body-outset
#| tbl-cap: "Summaries of data included in Model 1"
#| label: tbl-m1-data
msum <- function(x) {
  tibble(
    regions = ngrps(x)$region,
    countries = ngrps(x)$country,
    `year/country` = x$data %>%
      distinct(country, year) %>%
      count(country) %>%
      pull(n) %>%
      median(),
    nobs_internet = standata(x)$N_internet,
    nobs_outcome = standata(x)$N_val,
    outcome_range = str_glue(
      "{number(min(x$data$val), .01)} - {number(max(x$data$val), .01)}"
    )
  )
}
fits %>%
  mutate(summary = map(fit1, msum)) %>%
  select(outcome, summary) %>%
  unnest(summary) %>%
  kbl(caption = "Model 1 data summary") %>%
  kable_custom() %>% 
  row_spec(0, bold = TRUE)
```

#### Model checking

Now that the models are fit we proceed to check them. We only do this for the "prototypical" model 1, and so can discard the rest for the rest of this section

##### MCMC diagnostics

First we take a look at numeric summaries of convergence and posterior effective sample sizes. The former should approach 1, the latter should approach the number of hmc iterations.

We can see that the models have converged nicely, apart from the self-harm outcome.

```{r model-1-diagnostics}
#| results: hold
#| label: tab-model1-diagnostic
#| tbl-cap: "HMC Diagnostics, Model 1 population-level regression coefficients and country-level (co)variance parameters."
#| column: body-outset

diagnostic_table <- function(fit, rx, cp) {
  diag_1 <- fits %>%
    select(fit = {{ fit }}, outcome) %>% 
    mutate(
      out =
        map(
          fit,
          ~ as_draws_df(., variable = {{ rx }}, regex = TRUE) %>%
            summarise_draws(samples = length, default_convergence_measures())
        )
    ) %>%
    select(outcome, out) %>%
    unnest(out)
  diag_1 %>%
    kbl(
      caption = cp,
      digits = c(0, 0, 0, 2, 0, 0)
    ) %>%
    column_spec(
      4,
      color = "white",
      background = spec_color(
        log(diag_1$rhat),
        direction = 1,
        option = "C",
        end = .6
      )
    ) %>%
    column_spec(
      c(5, 6),
      color = "white",
      background = spec_color(
        log(diag_1$ess_tail / diag_1$samples),
        direction = 1,
        option = "C",
        end = 0,
        begin = .6
      )
    ) %>%
    kable_custom()
}
diagnostic_table(
  fit1,
  rx = c("^b_", "^sd_", "^cor_country__internet_year__val_year$"),
  cp = "Model 1 MCMC diagnostics."
) %>% 
  scroll_box(height = "300px")
```

##### Posterior predictive check

We then take a coarse look at how well the models reproduce the input data.

```{r ppcheck-density}

>>>>

# Preface {.unnumbered}

Welcome! This document is the online analysis supplement to *A global study of the association between internet adoption and adolescent mental health and well-being* (Vuorre & Przybylski, [Preprint]() in preparation). It contains all the analyses reported in the manuscript along with supplemental analyses. The data and source code repository, along with the datasets, are on [GitHub](https://github.com/digital-wellbeing/global-wbmh), and an archived permanent copy of these are on [OSF](https://osf.io/ys7m9/).

::: {.callout-note}
### How to reproduce our results

@@

1. Clone the github repo
  - Terminal: `git clone https://github.com/digital-wellbeing/global-wbmh.git`  
      OR
  - RStudio: File -> New Project -> Version Control -> Git -> use the URL from above

2. Prepare the R environment
  - Terminal: `Rscript -e "renv::restore()"`  
      OR
  - RStudio: Click renv -> Restore Library in the Packages panel

3. Render the source files to a Quarto book
 - Install [Quarto](https://quarto.org/docs/getting-started/installation.html) if you don't already have it
  - Terminal: `quarto render`  
      OR
  - RStudio: Open the project (`global-wbmh.Rproj`) and click Render in the Build panel

::: {.callout-important}
The project repo includes the GBD and ITU datasets, and **a synthetic mock version of the GWP dataset** to enable reproducing all our computations.
**The models take several hours each to run**---depending on your local computing resources---and therefore the rendering process can take several days. For this reason it might be easier to run the individual `.qmd` files interactively in RStudio.
:::

If something doesn't work please [open an issue](https://github.com/digital-wellbeing/global-wbmh/issues).
:::
